Critical Temperature of YBCO and BSCCO Superconductors

### 2014-11-25 Draft.tex
edits

\begin{abstract}
This article explains and illustrates the use of \LaTeX\ in preparing manuscripts
for submission to the American Journal of Physics (AJP). While it is not a
comprehensive reference, we hope it will suffice for the needs of most
AJP authors.
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

@@

Superconductivity has been found to occur in elements, alloys, binary compounds, and other materials.  
Roughly 70 years after superconductivity was discovered, ceramic materials with critical temperatures above the liquid nitrogen temperature of 77 K were found.\cite{melissinos} 
These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} 
In our experiment, we look at two high temperature superconductors, $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{n-1}\textrm{Cu}_{n}\textrm{O}_{9}$. %n=3 mainly for colorado superconductor 110 Tc

>>>>

\begin{abstract}
Superconductors are materials that lose their electrical resistance  when they fall below a certain temperature. This is called the critical temperature. We determine the critical temperatures of two superconductors,  $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, by measuring the voltage across the resistor as a function of temperature. 
\end{abstract}
% AJP requires an abstract for all regular article submissions.
% Abstracts are optional for submissions to the "Notes and Discussions" section.

@@

Superconductivity has been found to occur in elements, alloys, binary compounds, and other materials.  
Roughly 70 years after superconductivity was discovered, ceramic materials with critical temperatures above the liquid nitrogen temperature of 77 K were found.\cite{melissinos} 
These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} 
In our experiment, we look at two high temperature superconductors, $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ and $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, where $\textrm{n}=1,2,\textrm{ or},3$. %n=3 mainly for colorado superconductor 110 Tc
The amount of oxygen in $\textrm{Yt}\textrm{Ba}_{2}\textrm{Cu}_{3}\textrm{O}_{7-\delta}$ determines if the material will be superconducting. For $\textrm{Bi}_{2}\textrm{Sr}_{2}\textrm{Ca}_{\textrm{n}-1}\textrm{Cu}_{\textrm{n}}\textrm{O}_{9}$, the critical temperature is depends on the value of n.
